\texttt{nuance}: Detection of planetary transits in the presence of correlated noise

### 2023-01-19 simple/latex/ms.tex
finish first draft on nuance theory

% Define document class
\documentclass{aastex631}
\usepackage{float}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{bm}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\newpage
\section{\texttt{nuance}}\label{nuance}

In this section we describe \texttt{nuance}, an algorithm to search for planetary transits in light curves containing correlated noises, such as instrumental signals and stellar photometric variability. Our approach is based on \cite{foreman2016}, developed to detect planetary transits accounting for a linear model of systematics in K2 light curves. \texttt{nuance} differs by modeling the covariance of the light curve with a Gaussian Process, accounting for correlated noise (especially in the form of stellar variability) while keeping the model linear and tractable.\\

\subsection{Preamble}

The flux $f$ of a star measured at time $t$ is sampled and aranged in the $(1\times N)$ column-vector $\bm{f}$. This flux contains instrumental signals, stellar variability and a periodic transit signal that we wish to uncover. An example of such signal is simulated and shown in \autoref{fig:principle_dataset}.

@@

Simultaenously to the flux measurement, we obtained a set of $M$ measurements, aranged in the $(M\times N)$ matrix $\bm{X}$, that can be treated as explanatory variables for $\bm{f}$. Details about the simulation of these signals are provided in \autoref{app_principle_simulations}.
\\\\
Ideally, we would detect such  a periodic transit signal by sampling the posterior likelihood of this data to a full-fledge model including stellar variability (more generally correlated noises), instrumental systematics (modeled with explanatory variables), and a periodic transit signal of period $P$, epoch $T_0$, duration $D$ and depth $\Delta$. We would then reduce the posterior likelihood to $p(\bm{f}\vert P)$, its marginalized version over all parameters except the period $P$, producing a transit search periodogram $\mathcal{Q}(P)$. However, this approach has two issues: It is highly intractable, and it may lead to multimodal distributions that are hard to interpret.
\\\\
Given a period $P$, we instead want to compute the likelihood of a periodic transit signal at the maximum likelihood parameters $\bar T_0$, $\bar D$ and $\bar \Delta$, i.e the periodogram
\begin{equation}
    \mathcal{Q}(P) = p(\bm{f} \vert P, \bar T_0 ,\bar D, \bar \Delta)
\end{equation}
\begin{equation}
\text{where} \quad (\bar T_0 ,\bar D, \bar \Delta) = \argmax_{T_0, D, \Delta}p(\bm{f} \vert P, T_0 , D, \Delta)  
\end{equation}
We will do that by adopting the strategy of \cite{foreman2016}, and separate the transit search into two components: the \textit{linear search} and the \textit{periodic search}. During the \textit{linear search}, the likelihood of a single non-periodic transit is computed for a grid of epochs and durations (but not depths, as we will see). Then, the \textit{periodic search} consists in combining these likelihoods to compute the likelihood of the data given a periodic transit signal for a range of periods. These combined likelihoods yield a transit-search periodogram on which the periodic transit detection can be based.

\newpage
\subsection{The linear search}\label{linear_search}

During the linear search, the goal is to compute the likelihood $p(\bm{f} \vert T , D, \Delta)$ of our data given a single non-periodic transit signal of epoch $T$, duration $D$ and depth $\Delta$, for a grid of epochs, durations and (as we don't know yet) depths.
\\\\
To account for correlated noises, we model the light curve $f$ as being drawn from a Gaussian Process such that
$$\bm{f} \sim \mathcal{N}(\bm{w X}, \bm{\Sigma})$$
with mean $\bm{wX}$ (i.e. a linear model of the M explanatory variables with coefficients $\bm{w}$) and covariance $\bm{\Sigma}$. We append a non-periodic transit signal of epoch $T$, duration $D$ and unit depth (using the simple transit model from \citealt{protopapas}) as the last column of the design matrix $\bm{X}$, so that the transit is part of the linear model and the transit depth $\Delta$ can be solved linearly. Under this assumption, the log-likelihood of the data given a single non-periodic transit is analytical
\begin{equation} \label{eq:linear_search_ll}
    \ln p(\bm{f} \vert I) = -\frac{1}{2}(\bm{f}-\bm{wX})^T\bm{\Sigma}^{-1}(\bm{f}-\bm{wX}) -  \frac{1}{2}\vert\bm{\Sigma}\vert - \frac{N}{2}\ln 2
\end{equation}
and can be computed on a grid of epochs and durations only, since the transit depth is linearly solved for any $(T, D)$. This \textit{linear search} lead to the set of  log-likelihoods\footnote{This notation omits the vector $\bm{w}_{i,j}$ (except its last value $\Delta_{ij}$) as it is linearly solved for any given value of $(T_i, F_j)$ and irrelevant in what follows.}
$$\ln\mathcal{L} = \{\ln p(\bm{f} \vert T_i ,D_j, \Delta_{ij})\}_{i, j}$$
were $\Delta_{ij}$ is the depth linearly solved for a given $(D_i, T_j)$. \autoref{fig:linear_search} shows this likelihood grid computed for the simulated dataset shown in \autoref{fig:principle_dataset}. To compute this grid, we used the same Gaussian Process and design matrix $\bm{X}$ used to generate the data (see annexe).

\begin{figure}[H]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{../figures/principle_linear_search.pdf}
        \caption{Principle and output of the \textit{linear search}. First, a set of durations and depths $\{T_i, D_j\}_{i,j}$ is generated. For each pair of index $(i,j)$, the log likelihood $\ln p(\bm{f} \vert T_i ,D_j, \Delta_{ij})$ is computed, using the parameters from \autoref{eq:ls} and the expression of \autoref{eq:linear_search_ll}. This process yields the grid of log-likelihoods $\ln\mathcal{L}$ (bottom plot), as well as the $\{\Delta_{ij}, \sigma_{ij}\}_{i, j}$ transit depths and errors.}
        \label{fig:linear_search}
    \end{centering}
\end{figure}

To prepare the next step, the corresponding depths $\Delta_{ij}$ linearly solved for any $(T_i ,D_j)$ are conserved, as well as their associated errors $\sigma_{ij}$ obtained through the least-square solution

\begin{equation} \label{eq:ls}
    \begin{split}
        \bm{w} = (\bm{X}^T\bm{\Sigma}^{-1}\bm{X})^{-1}\bm{X}^T\bm{\Sigma}^{-1}\bm{f} \\
        \bm{\sigma} = (\bm{X}^T\bm{\Sigma}^{-1}\bm{X})^{-1}
    \end{split}
\end{equation}

where $\Delta_{ij} = \bm{w}_M$ and $\sigma_{ij} = \bm{\sigma}_{MM}$

\subsubsection{The periodic search}

We then need to combine the likelihoods computed from the linear search to obtain
\begin{equation}\label{eq:goal}
    p(\bm{f} \vert P, T_0 , D, \Delta)
\end{equation}
For a given transit duration $D$, any combination of $(P, T_0)$ leads to K truly independent transits, for which it is tempting to write
\begin{equation}
    p(\bm{f} \vert P, T_0 ,D, \Delta) = \prod_k^K p(\bm{f} \vert T_k, D, \Delta_k)
\end{equation}
where $\{T_k\}_k$ are the epochs matching $(T_0, P)$ and $\{\Delta_k\}_k$ the corresponding depths. So that
\begin{equation}
    \ln p(\bm{f} \vert P, T_0 ,D, \Delta) = \sum_k^K \ln \mathcal{L}_k
\end{equation}
This is the joint log-likelihood of transits belonging to the same periodic signal but with varying depths  $\{\Delta_k\}_k$. However, individual transits from a periodic signal cannot be considered independent, and should instead share a common transit depth $\Delta$. We show in \autoref{combining_transits} that there is an analytical expression for the joint log-likelihood of K individual transits with depths and errors $\{\Delta_k, \sigma_k\}_k$ under a common depth $\Delta$:
\begin{equation}\label{eq:comb}
    \ln p(\bm{f} \vert P, T_0 ,D, \Delta) =  \sum_{k}^K \ln \mathcal{L}_k  - \frac{K}{2}\ln(2\pi) - \frac{1}{2}\sum_k^K \left( \frac{\left(\Delta_{k} -
    \bar\Delta\right)^{2}}{\sigma_k^{2} + \sigma^{2}} + \ln{\left(\sigma_k^{2} + \sigma^{2} \right)} \right)
\end{equation}
\begin{equation}
    \text{with} \quad  
    \frac{1}{\sigma^2} = \sum_k^K \frac{1}{\sigma_k^2} \quad \text{and} \quad
    \Delta = \sigma^2 \sum_k^K {\frac{\Delta_k}{\sigma_k^2}}
\end{equation}
While this gives a solution for \autoref{eq:goal}\footnote{Different from the one found in \cite{foreman2016}}, its practical implementation raises two issues. One is that individual epochs matching ($T_0$, $P$) are not necessarily available in the grid of epochs $\{T_k\}_k$. In \cite{foreman2016} this is solved by using the nearest neighbors in the epochs grid. Instead, to allow the efficient computation of \autoref{eq:comb} in a vectorized form, we interpolate the likelihood grid from $\{T_i\}_i$ to a common grid of transit phases $\{\phi_i\}_i$, leading to the periodic search log-likelihoods $\mathcal{P}(P)$ (see \autoref{fig:periodic_search}).

\begin{figure}[H]
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{../figures/principle_periodic.pdf}
        \caption{On the example dataset, this figure shows how the periodic search work for any given period $P$. First, the log-likelihoods $\ln \mathcal{L}$ are phase-folded and interpolated onto a common grid of phases (the white lines mark the edges of each fold). Then \autoref{eq:comb} is computed on the full grid $\{\phi_i, D_i\}_i$ allowing the use of efficient matrix optimization.}
        \label{fig:periodic_search}
    \end{centering}
\end{figure}

The second and final issue is more fundamental, and lies in the fact that for each period we combine a different number of transits. Indeed, each likelihood $p(\bm{f} \vert T, D)$ estimated during the linear search is computed using N measurements. Hence, combining $K$ transits likelihoods in the periodic search, through $\Delta_k$ and $\sigma_k$ (\autoref{eq:comb}), artificially lead to a likelihood involving $N\times K$ measurements. While this problem could be set aside, it involves a normalization issue when trying to compare the joint log-likelihoods $\mathcal{P}(P)$ from one period to another (since for each period the number of observed transits is changing). This motivates a final step to produce the transit search periodogram.

\subsubsection{The transit periodogram}

To overcome the final issue presented in the last subsection, we will base our transit search periodogram not on the periodic transit likelihood computed for each period $P$, but on the real SNR of the periodic signal assesed

normalization
For a given period $P$, we can then compute $\max_{(T_0, D)}\{p(\bm{f} \vert P, T_0 ,D)\}$. But instead of relying on this maximum likelihood to build the final periodorgram, we compute the SNR of the transit with period $P$ and $(T_0, D)$ maximizing $p(\bm{f} \vert T_0 ,D, P)$, yielding the transit SNR periodogram shown in \autoref{fig:periodic_search}. We leave a discussion of this choice for Annexe .

\begin{figure}[H]
    \begin{centering}
        \includegraphics[width=0.8
        \linewidth]{../figures/principle_tiles_combined.pdf}
        \caption{}
        \label{fig:periodic_search}
    \end{centering}
\end{figure}

Once a transit recovered, we mask the corresponding epochs in the log likelihood linear grid

\subsubsection{An open-source python package}

@@

\appendix
\section{Light curve simulations}\label{app_principle_simulations}
\section{Combining transits}\label{combining_transits}

>>>>

% Define document class
\documentclass{aastex631}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{bm}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\set}[1]{\{\,#1\,\}}

@@

\section{\texttt{nuance}}\label{nuance}

In this section we describe \texttt{nuance}, an algorithm to search for planetary transits in light curves containing correlated noises, such as instrumental signals and stellar photometric variability.
\\\\
Let a flux $f$ of a star measured at time $t$ be sampled and aranged in the $(1\times N)$ column-vector $\bm{f}$. This flux contains instrumental signals, stellar variability and a periodic transit signal that we wish to uncover. An example of such signal is simulated and shown in \autoref{fig:principle_dataset}.

@@

Simultaenously to the flux measurement, we obtained a set of $M$ measurements, aranged in the $(M\times N)$ matrix $\bm{X}$, that can be treated as explanatory variables for $\bm{f}$. Details about the simulation of these signals are provided in \autoref{app_principle_simulations}.
\\\\
Ideally, we would detect such  a periodic transit signal by sampling the posterior likelihood of this data to a full-fledge model including stellar variability (more generally correlated noises), instrumental systematics (modeled with explanatory variables), and a periodic transit signal of period $P$, epoch $T_0$, duration $D$ and depth $\Delta$. We would then reduce the posterior likelihood to $p(\bm{f}\vert P)$, its marginalized version over all parameters except the period $P$, producing a transit search periodogram $\mathcal{Q}(P)$. However, this approach has two issues: It is highly intractable, and it may lead to multimodal distributions that are hard to interpret.
\\\\
Given a period $P$, we instead want to compute the likelihood of a periodic transit signal at the maximum likelihood parameters $\hat T_0$, $\hat D$ and $\hat \Delta$, i.e the periodogram
\begin{equation}\label{eq:periodogram}
        \begin{gathered}
        \mathcal{Q}(P) = p(\bm{f} \vert P, \hat T_0 ,\hat D, \hat \Delta) \\
        \text{where} \quad (\hat T_0 ,\hat D, \hat \Delta) = \argmax_{T_0, D, \Delta}p(\bm{f} \vert P, T_0 , D, \Delta)
    \end{gathered}
\end{equation}
We will do that by adopting the strategy of \cite{foreman2016}, and separate the transit search into two components: the \textit{linear search} and the \textit{periodic search}. During the \textit{linear search}, the likelihood of a single non-periodic transit is computed for a grid of epochs and durations (but not depths, as we will see). Then, the \textit{periodic search} consists in combining these likelihoods to compute the likelihood of the data given a periodic transit signal for a range of periods. These combined likelihoods yield a transit-search periodogram on which the periodic transit detection can be based. \texttt{nuance} differs by modeling the covariance of the light curve with a Gaussian Process, accounting for correlated noise (especially in the form of stellar variability) while keeping the model linear and tractable.

\subsection{The \textit{linear search}}\label{linear_search}

During the \textit{linear search}, the goal is to compute the likelihood $p(\bm{f} \vert T , D, \Delta)$ of our data given a single non-periodic transit signal of epoch $T$, duration $D$ and depth $\Delta$, for a grid of epochs, durations and depths.
\\\\
To account for correlated noises, we model the light curve $f$ as being drawn from a Gaussian Process such that
$$\bm{f} \sim \mathcal{N}(\bm{w X}, \bm{\Sigma})$$
with mean $\bm{wX}$ (i.e. a linear model of the M explanatory variables with coefficients $\bm{w}$) and covariance $\bm{\Sigma}$. To account for the presence of a single non-periodic transit of epoch $T$ and duration $D$, we compute and append its signal as the last column of the design matrix $\bm{X}$, using the simple transit model from \citealt{protopapas} with a unitary depth. This way, the transit signal is part of the linear model and its depth $\Delta$ can be solved linearly. Under this assumption, the log-likelihood of the data given a single non-periodic transit is analytical
\begin{equation} \label{eq:linear_search_ll}
    \ln p(\bm{f} \vert I) = -\frac{1}{2}(\bm{f}-\bm{wX})^T\bm{\Sigma}^{-1}(\bm{f}-\bm{wX}) -  \frac{1}{2}\vert\bm{\Sigma}\vert - \frac{N}{2}\ln 2
\end{equation}
and can be computed on a grid of epochs and durations, the transit depth being linearly solved for any $(T, D)$. This \textit{linear search} lead to the set of  log-likelihoods\footnote{This notation omits the vector $\bm{w}_{i,j}$ (except its last value $\Delta_{ij}$) as it is linearly solved for any given value of $(T_i, F_j)$ and irrelevant in what follows.}
$$\ln\mathcal{L} = \{\ln p(\bm{f} \vert T_i ,D_j, \Delta_{ij})\}_{i, j}$$
were $\Delta_{ij}$ is the depth linearly solved for a given $(D_i, T_j)$. \autoref{fig:linear_search} shows this likelihood grid computed for the simulated dataset shown in \autoref{fig:principle_dataset}, using the same Gaussian Process and design matrix $\bm{X}$ used to simulate the data (see annexe).

\begin{figure}[H]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{../figures/principle_linear_search.pdf}
        \caption{Principle and output of the \textit{linear search}. First, a set of durations and depths $\set{T_i, D_j}_{i,j}$ is generated. For each pair of index $(i,j)$, the log likelihood $\ln p(\bm{f} \vert T_i ,D_j, \Delta_{ij})$ is computed, using the parameters from \autoref{eq:ls} and the expression of \autoref{eq:linear_search_ll}. This process yields the grid of log-likelihoods $\ln\mathcal{L}$ (bottom plot), as well as the $\set{\Delta_{ij}, \sigma_{ij}}_{i, j}$ transit depths and errors.}
        \label{fig:linear_search}
    \end{centering}
\end{figure}

To prepare the next step, the corresponding depths $\Delta_{ij}$ linearly solved for any $(T_i ,D_j)$ are conserved, as well as their associated errors $\sigma_{ij}$ obtained through the least-square solution
\begin{equation}\label{eq:ls}
    \begin{gathered}
        \bm{w} = (\bm{X}^T\bm{\Sigma}^{-1}\bm{X})^{-1}\bm{X}^T\bm{\Sigma}^{-1}\bm{f} \\
        \bm{\sigma} = (\bm{X}^T\bm{\Sigma}^{-1}\bm{X})^{-1}
    \end{gathered}
\end{equation}    
where $\Delta_{ij} = \bm{w}_M$ and $\sigma_{ij} = \bm{\sigma}_{MM}$

\subsection{The periodic search}

We then need to combine the likelihoods computed from the \textit{linear search} to obtain
\begin{equation}\label{eq:goal}
    p(\bm{f} \vert P, T_0 , D, \Delta)
\end{equation}
For a given transit duration $D$, any combination of $(P, T_0)$ leads to K truly independent transits, for which it is tempting to write
\begin{equation}\label{eq:attempt}
    p(\bm{f} \vert P, T_0 ,D, \Delta) = \prod_k^K p(\bm{f} \vert T_k, D, \Delta_k)
\end{equation}
where $\set{T_k}_k$ are the epochs matching $(T_0, P)$ and $\set{\Delta_k}_k$ the corresponding depths. So that
$$
    \ln p(\bm{f} \vert P, T_0 ,D, \Delta) = \sum_k^K \ln \mathcal{L}_k
$$
This is the joint log-likelihood of transits belonging to the same periodic signal but with varying depths  $\set{\Delta_k}_k$. However, individual transits from a periodic signal cannot be considered independent, and should instead share a common transit depth $\Delta$. We show in \autoref{combining_transits} that there is an analytical expression for the joint log-likelihood of K individual transits with depths and errors $\set{\Delta_k, \sigma_k}_k$ assuming a common depth $\Delta$:
\begin{equation}\label{eq:comb}
    \begin{gathered}
        \ln p(\bm{f} \vert P, T_0 ,D, \Delta) =  \sum_{k}^K \ln \mathcal{L}_k  - \frac{K}{2}\ln(2\pi) - \frac{1}{2}\sum_k^K \left( \frac{\left(\Delta_{k} -
        \bar\Delta\right)^{2}}{\sigma_k^{2} + \sigma^{2}} + \ln{\left(\sigma_k^{2} + \sigma^{2} \right)} \right) \\
        \text{with} \quad  \frac{1}{\sigma^2} = \sum_k^K \frac{1}{\sigma_k^2} \quad \text{and} \quad
        \Delta = \sigma^2 \sum_k^K {\frac{\Delta_k}{\sigma_k^2}}
    \end{gathered}
\end{equation}
While this gives a solution for \autoref{eq:goal}\footnote{Different from the one found in \cite{foreman2016}}, the individual epochs matching $T_0$ and $P$ are not necessarily available in the grid of epochs $\set{T_k}_k$. In \cite{foreman2016} this is solved by using the nearest neighbors in the epochs grid. Instead, to allow the efficient matrix computation of \autoref{eq:comb}, we interpolate the likelihood grid from $\set{T_i}_i$ to a common grid of transit phases $\set{\phi_i}_i$, leading to the \textit{periodic search} log-likelihood
$$\ln\mathcal{P}(P) = \set{\ln p(\bm{f} \vert P, \phi, D)}_{i,j}$$
shown for few periods in \autoref{fig:periodic_search}.b, a notation where $\Delta_{ij}$ is omitted since being interpolated from the \textit{linear search} using $\phi_i$ and $D_j$, and $T_0 = 0$.

\begin{figure}[H]
    \begin{centering}
        \gridline{\fig{../figures/principle_periodic_0.pdf}{0.7\linewidth}{\vspace{-0.5cm}(a) $\ln \mathcal{L}$}}
        \vspace{-0.6cm}
        \gridline{\fig{../figures/principle_periodic_1.pdf}{0.6\linewidth}{\vspace{-0.5cm}(b) $\mathcal{P}(P)$}}
        \caption{On the example dataset, this figure shows how the \textit{periodic search} works at different periods $P$ (including the true period $P = 0.7$ days). Given $P$ and $T_0=0$, the log-likelihood $\ln\mathcal{L}$ shown in (a) is phase-folded and interpolated onto a common grid of phases shown in (b). As an example, the white lines in (a) mark the edges of each fold for a period of $P=0.5$ days, and the white crosses the epochs $\set{T_k}_{k\in\mathbb{K}}$ matching a particular phase in the grid (reported in (a) and (b)) on which the corresponding $\set{\ln \mathcal{L}_k}_{k\in\mathbb{K}}$ are interpolated and combined using \autoref{eq:comb}. To allow the use of efficient matrix computations, this is done for every duration $\set{D_i}_i$ so that $\mathcal{P}$ is computed on the full grid $\set{D_i, \phi_i}_{i, j}$ at once. We understand from plots in (a) that a different choice of epoch $T_0$ may only shift the results in phase but do not affect the values of $\mathcal{P}$. For this reason, computing $\mathcal{P}$ for $T_0=0$ is sufficient. We also notice how the maximum value of $\mathcal{P}(P=0.35)$ is lower than for $P=0.7$ days, a result of combining the log-likelihoods using \autoref{eq:comb} instead of \autoref{eq:attempt}, in favor of individual transits matching a common depth $\Delta$.}
        \label{fig:periodic_search}
    \end{centering}
\end{figure}

\subsection{The transit search periodogram}

Using \autoref{eq:comb}, we can now compute $\ln\mathcal{P}$ for a range of periods (see \autoref{fig:periodic_search}) and build a transit search periodogram using \autoref{eq:periodogram}. But a final issue emerges, one that is fundamentally linked to our strategy. Each likelihood $p(\bm{f} \vert T, D, \Delta)$ estimated during the \textit{linear search} is computed using N measurements. Hence, combining transits in the \textit{periodic search}, through $\Delta_k$, $\sigma_k$ and the product of $K$ likelihoods $\set{\mathcal{L}_k}_k$ (\autoref{eq:comb}), artificially leads to a likelihood involving $N\times K$ measurements. This lead to a normalization issue when trying to compare the joint log-likelihoods $\mathcal{P}(P)$ from one period to another (like the ones in \autoref{fig:periodic_search} that have been normalized for visualization purpose), as the number of observed transits differs from one period to another. This motivates a final step to produce the transit search periodogram $Q$.
\\\\
For any period P, instead of taking $ \mathcal{Q}(P)$ as the maximum value of $\ln\mathcal{P}$, we retrieve the maximum likekihood parameters
\begin{equation}\label{eq:phi0}
    (\phi_0 ,D) = \argmax_{\phi_i, D_j} \set{\ln p(\bm{f} \vert P, \phi_i, D_j)}_{i, j}
\end{equation}
and define $\mathcal{Q}(P)$ as the SNR of the transit of period $P$, epoch $T_0 = \phi_0 P$ duration $D$ and depth $\Delta$, i.e.
$$
    \mathcal{Q}(P) = \frac{\Delta}{\sigma}
$$
where $\Delta$ and $\sigma$ are obtained using \autoref{eq:comb} with the last column of $X$ containing a periodic transit signal of period $P$, epoch $T_0$, duration $D$ and depth $1$. This process and the resulting periodogram $\mathcal{Q}$ are shown in \autoref{fig:periodogram}.

\begin{figure}[H]
    \begin{centering}
        \includegraphics[width=0.62\linewidth]{../figures/principle_Q.pdf}
        \caption{}
        \label{fig:periodogram}
    \end{centering}
\end{figure}

The periodic transit of period $P$ with the maximum SNR, i.e. maximizing $\mathcal{Q}$, is adopted as the best candidate, adapting our confidence through the minimum SNR for which we consider a signal to be real. The parameters of this transit are the period $P$, the epoch $T_0 = \phi_0 P$ and duration $D$ (\autoref{eq:phi0}), and the depth $\Delta$ with error $\sigma$ (\autoref{eq:comb}).

\newpage
\subsubsection{An open-source python package}

@@

\newpage
\appendix
\section{Light curve simulations}\label{app_principle_simulations}
\section{Combining transits}\label{combining_transits}
